\section*{\centering{Abstract}}
Beyond wave detection, smartsolo geophones are furnished with a wide array of 
sensors that provide data necessary for signal processing seismic data, 
sensors that provide data about orientation and position, recieved by gps, 
as well as temperature, an adjustable gain and sample rate, 
damping coefficients, and more. Metadata from these systems are dumped into a text file, 
along-side a miniseed encoding that stores the actual seismic detection. 
By providing such a broad arrangement of metadata, SmartSolo geophones can be deployed 
simply and flexibly, in contrast to devices that require far more extensive testing for identifying theirfrequency response, geographic surveying 
to be precisely positioned, sheltering to keep a constant temperature, and other challenges. While such single stations, having been deployed at wide distances all around the globe,
are ideal for identifying the hypocenters of major seismic events, SmartSolo arrays are more ideal for local deployment, able to detect smaller but more proximal events.
This makes them ideal for seismic surveying with intent to identify local fracture networks, induced seismicity, shear wave splitting, or similar interests.
By their configurability and flexibility can the SmartSolos provide seismic data suited to the particular needs of a survey. 
 However, some technical understanding is necessary to determine the proper settings necessary before deployment in order for data to be collected that best suits 
 the particular details of the expermint. 
Furthermore, once  the smartsolo data is collected, the challenge remains for it to be properly processed. Making appropriate decisions to meet these challenges require a combined application of data science, physics, and signal processing,
in order for a SmartSolo array to be deployed at its full potential.  
Fortunately, multiple packages for python are available to greatly simplify the work.  This report will discuss in detail the challenges of 
seismic signal processing with smartsolo geophones, scripts in python with the packages available to overcome them, and experiments already performed with the smartsolos.
 Spectrograms, timeseries, geographic maps, bode plots, and cross correlations
have all been generated for discussion and analysis of the data collected during a smartsolo deployment of twelve geophones. 

